Download data

### 2023-12-30 scripts/download_independent_variables.Rmd
replacing NA with biological 0 in 3 rasters
processedsed earthenv landcover

rm(gdgfgd10, gdgfgd5, swe, p, paths, maskR)
```

>>>>

rm(gdgfgd10, gdgfgd5, swe, p, paths, maskR, filename, template)
```

make tiles of shrub and herbaceous cover, and create total percent tree cover layers

```{r}
p <- '/media/steppe/hdd/Geospatial_data/WesternPlantPredictors2/chelsa/bio1'
bio1 <- vrt(file.path(p, list.files(p))) # use this for resampling.

p <- '/media/steppe/hdd/Geospatial_data/earthenv'
f <- list.files(p)

shrub <- vrt(file.path(p, f[5]))
shrub <- crop(shrub, project(domain, crs(shrub)))
shrub <- project(shrub, 'EPSG:5070')
shrub <- resample(shrub, bio1)

pout <- '/media/steppe/hdd/Geospatial_data/WesternPlantPredictors2/veg_cover'
filename <- paste0(pout, '/shrub/', 'shrub_.tif')
makeTiles(shrub, template, filename)
rm(shrub)

herbs <- vrt(file.path(p, f[6]))
herbs <- crop(herbs, project(domain, crs(herbs)))
herbs <- project(herbs, 'EPSG:5070')
herbs <- resample(herbs, bio1)

filename <- paste0(pout, '/herb/', 'herb_.tif')
makeTiles(herbs, template, filename)
rm(herbs)

layers <- lapply(file.path(p, f[1:4]), vrt)
layers <- rast(layers)

layers <- crop(layers, project(domain, crs(layers)))
layers <- project(layers, 'EPSG:5070')
layers <- resample(layers, bio1)

tree <- sum(layers)
filename <- paste0(pout, '/tree/', 'tree_.tif')
makeTiles(tree, template, filename)
rm(tree, layers)

rm(p, f, pout, filename)
```
